Handling Recursion in Generic Programming Using Closed Type Families

### 2018-04-25 lncs-paper.tex
Fix an error in RW

Several works show how to define the Zipper~\cite{Huet1997} generically for regular~\cite{HiJeLo2004,McBride2001}, mutually recursive~\cite{MuRec2009}, and heterogeneous~\cite{Adams2010} types using fixed-point generic views.

>>>>

Several works show how to define the Zipper~\cite{Huet1997} generically for regular~\cite{HiJeLo2004,McBride2001} and mutually recursive~\cite{MuRec2009} types using fixed-point generic views. Adams~\cite{Adams2010} defines a generic zipper for heterogeneous types.
